### 2016-01-24 Projects/DelCo_2012/Report/DelCo_2012.tex
minor edit to CAFS

>>>>

\subsubsection{Furniture Fuel Package}
\label{sec:fire_suppression_furniture_fuel_2}

The fuel load for two of the experiments consisted of 3 sofas, carpet, padding, and oriented strand board (OSB) paneling along the East, West, and South walls and ceiling. The three couches are aligned along the West wall and spaced 1.2~m (4~ft) apart. The specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:furniture_2story}. In total, this fuel package contains approximately {\bf XXX} fuel consisting of wood, polyurethane (PU), polyester (PET),and polyprolene (PP).

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Pallets}
	\caption{Furniture Fuel Load in First Floor of Two-Story Structure.}
	\label{fig:furniture_2story}
\end{figure

\subsubsection{Furniture and Pallet Fuel Package}
\label{sec:fire_suppression_combo_fuel_2}
